\subsection{Research}

When completing this research the focus has been on one particular dataset from the CRAWDAD archive. This dataset was chosen because it is one of the most popular datasets in the archive, having been cited by 374 papers at the time of writing \cite{aboutCrawdad2014}. The most frequently cited dataset however is cambridge/haggle, the reasoning for deciding not to focus on this instead is that the Cambridge dataset is comparatively small in size and would therefore benefit much less from the summarisation which this project hopes to provide.
\newline
The papers that have been selected for use in this research were chosen because they all cite the dartmouth/campus dataset. A simple online search was used to retrieve the most recent papers citing the chosen dataset, this was how all papers aside from \cite{Wei2013} and \cite{Feng2012} were selected. The remaining papers were chosen based on aiming to include all apparent general areas of research that have used the dartmouth/campus dataset in the past 9 years. Table \ref{usageTable} shows a summary of the type of information each paper needed to use from the dartmouth/campus dataset.

\input{usage_table.tex}

\subsection{Summary of Results}
The usage of the Dartmouth University CRAWDAD dataset is primarily regarding network mobility and DTNs. As such, the most often needed information seems to be identifiers (mainly IP addresses) for both mobile devices and access points, and the times of connections.

There is also research into SDN and wide-band small-cell networking using the dartmouth/campus dataset. These uses seem to require a wider variety of information from the data, however these instances are much less frequent than those mentioned above. Bandwidth, quality of connection, and MAC address are only mentioned in these less common cases.