\subsubsection{Research}

When completing this research the focus has been on one particular dataset from the CRAWDAD archive, dartmouth/campus \cite{dartmouthcampus2009}. This dataset was chosen because it is one of the most popular datasets in the archive, having been cited by 374 papers at the time of writing \cite{aboutCrawdad2014}. The most frequently cited dataset however is cambridge/haggle, the reasoning for deciding not to focus on this instead is that the Cambridge dataset is comparatively small in size and would therefore benefit much less from the summarisation which this project hopes to provide.
\newline
The dartmouth/campus dataset is collected over Dartmouth College's network. It is comprised of five years worth of data collected using various methods; tcpdump, syslog, and SNMP. As the tcpdump data is largest and most unfiltered, it would benefit most from this summarisation, and will be the initial focus. This data includes pcap files containing the headers of all transmissions sent via the Dartmouth College network from 27 on-campus buildings. More detailed information regarding the Dartmouth network can be found on the CRAWDAD website \cite{dartmouthcampus2009}.
\newline
The papers that have been selected for use in this research were chosen because they all cite the dartmouth/campus dataset. A Google Scholar \cite{googleScholar} online search was used to retrieve the most ``relevant" papers which used the chosen dataset, from these results the ones which have been most often cited in other work were selected. This selection process found papers which are relevant in the research community. As there are different versions of the dataset the search had to be repeated three times, once using the 2009 dataset, once with the 2007 dataset, and once with the 2005 dataset. For each search the five most cited results have been used. Table \ref{usageTable} shows a summary of the type of information each paper needed to use from the dartmouth/campus dataset. Papers in which the dataset was referenced but ultimately has not been used have been excluded.

\input{context/usage_table.tex}

\subsubsection{Summary of Results}
The usage of the Dartmouth College CRAWDAD dataset is primarily regarding network mobility and social interaction/encounters. As such, the most often needed information seems to be identifiers for both mobile devices and access points, and the times of connections. Network mobility is a term used to refer to the connectivity and movement of users between multiple access points. Example usage of mobility research may be a Dartmouth College student wishing to stay connected to the internet while walking around their accommodation block and moving between areas which are covered by different access points, or a system may wish to offload a task but needs to be able to expect certain location-based conditions for it to be worthwhile. DTNs aim to eliminate the issues caused by intermittent connectivity, such as is found when moving between multiple access points. The Dartmouth College data is popular for this type of research since it reflect real-life usage of a large network. Also, the buildings from which data was collected include accommodation as well as academic buildings and so can provide insight into different types of usage.
I found that the majority of the papers I looked at used the movement \cite{dartmouthcampus2009movement} or syslog \cite{dartmouthcampus2009syslog} tracesets as these are most tailored towards mobility research. 

There are also some less frequent topics of research such as software defined networking and delay tolerant networking using the dartmouth/campus dataset. These uses seem to require a wider variety of information from the data, however these instances are much less frequent than those mentioned above. these less common cases are the only ones which mention bandwidth and quality of connection.

